Open-source tools in R for landscape ecology

### 2020-12-20 paper/paper.Rmd
improves figures

ggplot_usefulness <- ggplot(data = usefulness_df) +
  geom_bar(aes(x = usefulness_class, y = n_rel), 
           stat = "identity") + 
  theme_classic(base_size = 10) +
  theme(plot.title.position = "plot") +
  scale_y_continuous(breaks = seq(0, 60, 10), limits = c(0, 60)) + 
  guides(fill = FALSE, colour = FALSE) +
  labs(x = NULL,
       title = "How useful do you think is R currently for landscape ecology?", 
       y = "Number of participants [%]")
```

@@

```{r fig-survey, echo = FALSE, fig.align="center", fig.cap = "Results of the online survey about open-source software tools in R for landscape ecology. Results include A) which terms describe major reserach topics the best, B) the most important workflow task, C) the most used R packages and D) the overall usefulnes or R for landscape ecology. 'others' includes all answers with less than five total mentions.", warning=FALSE}

(ggplot_topics | ggplot_tasks | ggplot_packages ) / ggplot_usefulness + 
  plot_layout(heights = c(2, 3)) +
  plot_annotation(tag_levels = "A", tag_suffix = ")")

>>>>

ggplot_usefulness <- ggplot(data = usefulness_df) +
  geom_bar(aes(x = usefulness_class, y = n_rel), 
           stat = "identity") + 
  theme_classic(base_size = base_size) +
  theme(plot.title.position = "plot") +
  # scale_x_continuous(breaks = seq(0, 60, 10), limits = c(0, 60)) +
  guides(fill = FALSE, colour = FALSE) +
  labs(x = NULL,
       title = "How useful do you think is R currently\nfor landscape ecology?", 
       y = "Number of participants [%]") +
  coord_flip()
```

@@

```{r fig-survey, echo = FALSE, fig.align="center", fig.cap = "Results of the online survey about open-source software tools in R for landscape ecology. Results include A) which terms describe major reserach topics the best, B) the most important workflow task, C) the most used R packages and D) the overall usefulnes or R for landscape ecology. The 'others' category includes all answers with less than five total mentions.", warning=FALSE, out.width="100%"}

(ggplot_topics | ggplot_tasks) / (ggplot_packages | ggplot_usefulness) + 
  # plot_layout(heights = c(2, 3)) +
  plot_annotation(tag_levels = "A", tag_suffix = ")")
